Hydras \& Co.

### 2022-09-09 doc/chapter-encoding.tex
work on the chapter on goedel encodings; new exercise

  \begin{exercise}
  Give a new equivalent definition of \texttt{codeNth}, without using tactics like \texttt{assert}.  You may define an help function for this purpose, in which case, please specify what your helper computes.
  \end{exercise}

>>>>

   \index{hydras}{Exercises}
  \begin{exercise}
  Give a new equivalent definition of \texttt{codeNth}, without using tactics like \texttt{assert}.  You may define an help function for this purpose, in which case, please specify what your helper computes.
  \end{exercise}

     \index{hydras}{Exercises}
  \begin{exercise}
    Please consider the following definition:

    \inputsnippets{OnCodeList/membersDef}

    \noindent

    Prove that the functions \texttt{codeList} and \texttt{members} are inverse of each other.
  \end{exercise}

  \subsection{Strong recursion}

  List encoding helps us to define primitive recursive functions
  where the computation of $f\;n$ may  depend of
  [part of] the values $f\;0$, $f\;1$, \dots, $f\;(n-1)$.

  A simple example is the \texttt{div2} function
  defined by
  \begin{align*}
    \texttt{div2}\;0&=0\\
    \texttt{div2}\;1&=1\\
    \texttt{div2}\;(n+2)&=S(\texttt{div2}\;n)\\
  \end{align*}

  The trick is to define a helper $h$ where
  $h\;n\;a$ is the natural number which represents
  the sequence $\langle \texttt{div2}(n-1),
  \texttt{div2}(n-2),\dots,\texttt{div2}\;1, \texttt{div2}\;0\rangle$.

  In \coq, the helper associated with \texttt{div2} is defined in
  \href{../theories/html/hydras.MoreAck/PrimRecExamples}{MoreAck.PrimRecExamples}.

  \inputsnippets{PrimRecExamples/fdiv2Def}

  The function \texttt{(evalStrongRec\;$n$\;$h$\;$c$)} computes
  $(f\;c)$ if $h$ is the helper associated with $f$.

  \inputsnippets{PrimRecExamples/fdiv2Examples}

  This function is defined in
  \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair}.
   Definitions and related lemmas are quite tricky, but look easy to apply.

   \inputsnippets{cPair/evalStrongRecDef}

   \inputsnippets{cPair/evalStrongRecPR}
    \inputsnippets{cPair/computeEvalStrongRecHelp}
